Synthesizing Symmetric Lenses

### 2018-07-12 papers/SymmetricLenses/main.tex
add more text and cleaning

%\newif\ifdraft\drafttrue  % set true to show comments
\newif\ifdraft\draftfalse  % set true to show comments
\newif\ifanon\anonfalse    % set true to suppress names, etc.
\newif\iffull\fullfalse   % set true for long version
\newif\ifappendices\appendicestrue

@@

Adjusting the termination parameter was needed in only 9 of the 48 tasks. In practice, we
found that customizing the termination metric to be quite easy: if manual
inspection of the lens showed there were too few bijections, we would increase
the termination parameter. If synthesis took too long, we would decrease it.
Section~\ref{subsec:effect-of-heuristics}, studies the effect of fixing the
termination metric.

@@

Recall that compositional synthesis exploits user annotations to break a
benchmark into a series of smaller synthesis steps. In our experience,
compositional synthesis (SS mode) allows our system to scale to arbitrarily
large and complex formats; measuring it provides an estimate of the
responsiveness of the system when used as intended.\saz{Anders check this!} However, SSNC mode, which
uses no such annotations and synthesizes a complete lens all at once provides a
useful experimental stress test for the system.

@@

For each benchmark in the suite and each mode, we ran the system with a timeout
of 60 seconds, averaging the result over 5 runs.  Figure~\ref{fig:times}
summarizes the results of these tests. We find that our algorithm is able to
synthesize all of the benchmarks in under 30 seconds. Without compositional
synthesis, the synthesis algorithm is able to solve only 26 problem
instances.

>>>>

%\newif\ifdraft\drafttrue  % set true to show comments
\newif\ifdraft\draftfalse  % set true to show comments
\newif\ifanon\anonfalse    % set true to suppress names, etc.
\newif\iffull\fullfalse   % set true for long version
\newif\ifappendices\appendicesfalse

@@

Adjusting the termination parameter was needed in only 9 of the 48 tasks. In practice, we
found that customizing the termination metric to be quite easy: if manual
inspection of the lens showed there were too few \IdentityLens{}s, and too many
\Disconnect{}s or merges, we would increase
the termination parameter. If synthesis took too long, we would decrease it.
Section~\ref{subsec:effect-of-heuristics} studies the effect of fixing the
termination metric.

@@

Recall that compositional synthesis allows users to break a benchmark into a
series of smaller synthesis tasks, whose solutions are utilized in more complex
synthesis procedures. Compositional synthesis (\SSOpt{} mode)
allows our system to scale to arbitrarily large and complex formats; measuring
it shows of the responsiveness of the system when used as
intended. \SSNCOpt{} mode, which synthesizes a complete lens all at once,
provides a useful experimental stress test for the system.

@@

For each benchmark in the suite and each mode, we ran the system with a timeout
of 60 seconds, averaging the result over 5 runs. Figure~\ref{fig:times}
summarizes the results of these tests. We find that our algorithm is able to
synthesize all of the benchmarks in under 30 seconds. Without compositional
synthesis, the synthesis algorithm is able to solve 26 problem instances.
